Refinements for open automata

### 2022-06-27 2021-Refinement/paper/refinementarticle.tex
proof meeting notes

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}
Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\Big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
 \TODO{to check why $j \in J'_2 \setminus\{k\}$}

@@

The proof continues as described above.

-------------------------------\\

\TODO{NEW PROOF SKETCH}
HYPOTHESES and OBJECTIVES

TWO cases for the OT $t_{23}$

CASE 1 : $k$ does not move in $A_2$

two cases for  $t_{13}$

 ...

in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ does not move

and has the desired property for ``relation is preserved along identical transitions''

CASE 2 : k moves in $A_2$ with action $\beta_{2 k}$, and $A_3$ does the labelled action $\beta_{2 k}$.

two cases for  $t_{13}$

 ...

in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ should move with the action $\beta_{2 k}$.

We recompose a $t_{1}'$ with $t_{1}'$ and $t_3$ from  $t_{23}$

it has the desired property for ``relation is preserved along identical transitions''

relation on guards should hold but to be formulated carefully.

\TODO{END OF NEW PROOF SKETCH}
\begin{comment}
 $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}

>>>>

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}
Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\Big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\Big) \wedge g^2_3 \\
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}

@@

The proof continues as described above. \TODO{finish the proof}

\begin{comment}
 $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
\begin{multline*}
 \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
\end{multline*}
